Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-20 paper/paper.tex
comparison with Vollmer

\subsubsection{Comparison with other tools}\Mar{Lucas and Guilherme,
  please summarize results here!}

>>>>

\subsubsection{Comparison with other tools}
 \Luc{Vollmer \cite{vollmer-etal-cics2011} used and evolutionary approach to 
autonomously generate rules to detect ICMP packets using the Snort IDS. They built their own dataset 
using packet creation tools. Ten different packets were 
created to match ten existing rules, and then these packets were used as input 
to the rule generation. As a result, they were able to produce rules with 
100\% detection rate and that produced 3 false positives out of 33k packets.
On our experiments with Syrius, we used 381 \Fix{use macros}packets that matches nine existing 
rules and it was able to generate rules that detected all the packets with 
no false positives.  
 }

 \Luc{Guruprasad \cite{guruprasad}}
